ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-09 pyked.tex
Add link to example notebooks in GitHub

The following usage examples provide a guide to the use of \pk{}. They are by no
means an exhaustive treatment, and are meant to demonstrate the basic
capabilities of the software.

>>>>

The following usage examples provide a guide to the use of \pk{}. They are by no means an exhaustive
treatment, and are meant to demonstrate the basic capabilities of the software. Both examples shown
below are also available as Jupyter Notebook files from the GitHub repository for
PyKED\footnote{\url{https://github.com/pr-omethe-us/PyKED/blob/master/docs/rcm-example.ipynb} and
\url{https://github.com/pr-omethe-us/PyKED/blob/master/docs/shock-tube-example.ipynb}} and in the
Supplementary Material associated with this article.
